Method 1: Separate Regressions

Step 1. Simulate Xi = (x1, x2, ..., xn) from a known distribution (uniform, poisson, normal).

Step 2. Given Xi, simulate (Yi(0), Yi(1)) from a known distribution (normal, with constant/Xi-related variance) where E(Yi(t) | Xi) is a linear combination of Xi, t = 0 or 1.

Step 3. Assign 0 or 1 equally possible and independent of Y to Ti. Consider 1 as treated and 0 as given placebo.

Step 4. Denote miut(x) as E(Y(t) | X = x). Regress all Yi(0) on Xi where Ti = 0 to get miuhat0(x), and regress all Yi(1) on Xi where Ti = 1 to get miuhat1(x).

Step 5. Denote tao(x) = miu1(x) - miu0(x). MSE on taohat(x).

```{r}
#Step 1.

age <- rpois(1000, 27)
sex <- rbinom(1000, 1, 0.5) #0 as female
race <- round(runif(1000, 0, 4))
race[which(race==4)] <- 0 #has 4 type: 0: Asian; 1: Black; 2: White; 3: Hispanic
race[which(race==0)] <- "Asian"
race[which(race==1)] <- "Black"
race[which(race==2)] <- "White"
race[which(race==3)] <- "Hispanic"

#Step 2.

race0 <- c(1000, 0)
race0[which(race=="Asian")] <- 50000 #Asians are specially sensitive to this disease
race0[which(race=="Black")] <- 1000 #Blacks are relatively "immune"
race0[which(race=="White")] <- 20000
race0[which(race=="Hispanic")] <- 10000
y0 <- 1000 * age + 5000 * sex + race0 + rnorm(1000, 0, 1000)

race1 <- c(1000, 0)
race1[which(race=="Asian")] <- 5000 #Asians are easily cured
race1[which(race=="Black")] <- 500
race1[which(race=="White")] <- 15000 #Whites are insensitive to treatment
race1[which(race=="Hispanic")] <- 5000
y1 <- 10 * age + 100 * sex + race1 + rnorm(1000, 0, 50)

#Step 3.

t <- rbinom(100, 1, 0.5) #0 as given placebo
```

```{r}
A <- data.frame(y0, y1, t, age, sex, race)
A
```

```{r}
#Step 4.

A0 <- subset(A, t == 0)
miuhat0 <- lm(y0 ~ age + sex + race, data = A0)
A1 <- subset(A, t == 1)
miuhat1 <- lm(y1 ~ age + sex + race, data = A1)

miuhat0
#The true model is y0 = 1000*age + 5000*sex + 50000*Asian + 1000*Black + 20000*White + 10000*Hispanic + N(0, 1000)
miuhat1
#The true model is y1 = 10*age + 100*sex + 5000*Asian + 500*Black + 15000*White + 5000*Hispanic + N(0, 50)
#both fit well.
```

```{r}
#Step 5.

EY1 <- as.vector(as.matrix(cbind(age, sex, race1)) %*% c(10, 100, 1))
EY0 <- as.vector(as.matrix(cbind(age, sex, race0)) %*% c(1000, 5000, 1))
EY1hat <- predict(miuhat1, A[4:6])
EY0hat <- predict(miuhat0, A[4:6])
MSE <- sum(((EY1 - EY0) - (EY1hat - EY0hat)) * ((EY1 - EY0) - (EY1hat - EY0hat))) / 999
MSE
```





Method 2: Same Regressions

```{r}
B <- data.frame(yobs = rep(0, 1000), y0, y1, t, age, sex, race)
B$yobs[B$t == 0] <- B$y0[B$t == 0]
B$yobs[B$t == 1] <- B$y1[B$t == 1]
B
```

```{r}
miuhat <- lm(yobs ~ t + age + sex + race, data = B)
miuhat
```

```{r}
EY1 <- as.vector(as.matrix(cbind(age, sex, race1)) %*% c(10, 100, 1))
EY0 <- as.vector(as.matrix(cbind(age, sex, race0)) %*% c(1000, 5000, 1))
EY1hatB <- predict(miuhat, data.frame(t = 1, B[5:7]))
EY0hatB <- predict(miuhat, data.frame(t = 0, B[5:7]))
MSE <- sum(((EY1 - EY0) - (EY1hatB - EY0hatB)) * ((EY1 - EY0) - (EY1hatB - EY0hatB))) / 999
MSE
```




Method 3: Modified Outcome Regression.

```{r}
C <- B
C$yobs[C$t == 0] <- -2 * C$y0[C$t == 0]
C$yobs[C$t == 1] <- 2 * C$y1[C$t == 1]
C
```

```{r}
miuhatC <- lm(yobs ~ age + sex + race, data = C)
miuhatC
```

```{r}
EY1 <- as.vector(as.matrix(cbind(age, sex, race1)) %*% c(10, 100, 1))
EY0 <- as.vector(as.matrix(cbind(age, sex, race0)) %*% c(1000, 5000, 1))
taohatC <- predict(miuhatC, C[5:7])
MSE <- sum(((EY1 - EY0) - taohatC) * ((EY1 - EY0) - taohatC)) / 999
MSE
```


